`State and Parameter Estimation for Spatio-Temporal Neural Fields' or `A Data Driven Framework for Patient-Specific Neural Field Modelling'

### 2010-06-21 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
changed appendix B

\begin{equation}\label{eq:AppendixWt} 

@@

\section{}\label{ColoredNoise} 
\newtheorem{lemma}{Lemma} 
\begin{lemma}
	Consider the i.i.d. noise term $e_t(\mathbf{r})\sim\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r'}))$ then 
	\begin{equation}\label{eq:AppendixWt} 
		\mathbf e_t(\mathbf r)=\boldsymbol{\Gamma}^{-1}\int_\Omega {\boldsymbol{\phi} ( \mathbf{r} )e_t( \mathbf{r} )d\mathbf{r}} 
	is a vector valued, zero mean normally distributed white noise process with covariance 
		\boldsymbol\Sigma_e =\mathbf{\Gamma}^{-1}\int_{\Omega}\int_{\Omega}\boldsymbol{\phi}\left(\mathbf r\right) \gamma\left(\mathbf r- \mathbf r' \right)\boldsymbol{\phi}\left(\mathbf r'\right)^{\top}d\mathbf r' d\mathbf r\mathbf{\Gamma}^{- \top} 
	\label{lemma:FieldCovariance} 
\end{lemma}
\section*{Proof} Equation (\ref{eq:AppendixWt}) is a linear function of $e_t(\mathbf r)$ and hence $\mathbf{e}_t$ is also normally distributed. The expected value of $\mathbf e_t(\mathbf r)$ is given by 

@@

	\mathbf E\left[ \mathbf e_t(\mathbf r)\right]&=& \mathbf{\Gamma}^{-1}\int_{\Omega}\boldsymbol\phi\left(\mathbf{r}\right)\mathbf E\left[e_t\left(\mathbf{r}\right)\right] d\mathbf{r} \nonumber \\

@@

The covariance of $\mathbf{e}_t(\mathbf r)$ is 

@@

	\lefteqn{\mathbf E\left[ \mathbf e_t(\mathbf r) \mathbf e_t^\top(\mathbf r')\right]} \nonumber \\ 

>>>>

\begin{equation}\label{eq:Wt} 

@@

\section{Mean and covariance of the state disturbance }\label{ColoredNoise} 
State disturbance defined in equation~\ref{eq:Wt} is a linear function of $e_t(\mathbf r)$ and hence $\mathbf{e}_t$ is also normally distributed. The expected value of $\mathbf e_t$ is given by 

@@

	\mathbf E\left[ \mathbf e_t\right]&=& \mathbf{\Gamma}^{-1}\int_{\Omega}\boldsymbol\phi\left(\mathbf{r}\right)\mathbf E\left[e_t\left(\mathbf{r}\right)\right] d\mathbf{r} \nonumber \\

@@

The covariance of $\mathbf{e}_t$ is 

@@

	\boldsymbol\Sigma_e =\lefteqn{\mathbf E\left[ \mathbf e_t\mathbf e_t^\top\right]} \nonumber \\ 
